---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
options(width = 100)
```

# rankprob

<!-- badges: start -->
<!-- badges: end -->

`rankprob` facilitates the computation of the predicted probability of a given ranking of choices from the output of a multinomial regression model, in particular, making it easy to use these predicted probabilities in `marginaleffects` and `clarify`. It does so by providing a new type of prediction for multinomial models, which is activated by running `convert_rankprob()` on the multinomial or ordinal regression output object, e.g., the output of a call to `nnet::multinom()`, `MASS::polr()`, or `WeightIt::multinom_weightit()`.

## Installation

You can install the development version of `rankprob` from [GitHub](https://github.com/ngreifer/rankprob) with:

``` r
# install.packages("pak")
pak::pak("ngreifer/rankprob")
```

## Example

Below, we use `rankprob` to transform the output of `nnet::multinom()` to compute the predict probability of two ordered rankings and the average marginal effect of the predictors on the probability of a given ranking.

```{r example, warning=FALSE}
library(rankprob)

set.seed(123)
n <- 500
data <- data.frame(x1 = rnorm(n),
                   x2 = rnorm(n),
                   x3 = factor(sample(c("t", "c"), n, replace = TRUE)),
                   y = sample(LETTERS[1:4], n, TRUE))

fit <- nnet::multinom(y ~ x1 + x2 + x3, data = data,
                      Hess = TRUE, trace = FALSE)

fit <- convert_rankprob(fit)

p <- predict(fit, rankings = list(c("A", "B", "C", "D"),
                                  c("B", "A", "D", "C")))

head(p)

marginaleffects::avg_slopes(fit, type = "rank_probs",
                            rankings = list(c("A", "B", "C", "D")))
```
